mathml: Translate R expressions to MathML and LaTeX/MathJax

### 2022-12-11 Draft3.Rmd
integrate

In the second example, Here we present a second less trivial example where Prolog needs to find out the name of
the integration variable for `sin`. For that purpose, \pkg{rolog} provides a predicate `r_eval/2` that calls R from Prolog. Here, the predicate is used for the  R\ function `formalArgs(args(sin))`, which returns the name of the function argument of `sin`, that is, `x`.

```{r,  results = 'asis', echo = TRUE}
term = quote(integrate(sin, 0L, 2L*pi))
mathout(term)
```

```{r, echo = TRUE}
eval(term)
```

Note that, on the Prolog end, the handler for `integrate/3` is rather rigid; it
accepts only these three arguments in that particular order, and without names,
that is, `integrate(sin, lower=0L, upper=2L * pi)`, would not print the desired
result.

Therefore, `pl/mathml.pl` includes two handlers that accept terms with named
arguments, `integrate(f=Fn, lower=Lower, upper=Upper)`, as well as terms of the
form `$(integrate(Fn, Lower, Upper), value)` that are needed for the evaluation
below.

>>>>

## Ringing back to R

R's `integrate` function takes a number of arguments, the most important ones
being the function to integrate, and the lower and the upper bound of the
integration. For mathematical typesetting in the form
of $\int f(x)\, dx$, \pkg{mathml} needs to find out the name of the integration
variable. For that purpose, the underlying Prolog bridge provides a
predicate `r_eval/2` that calls R from Prolog. In the example below, this
predicate is used for a call of `formalArgs(args(sin))`, which returns the names
of the function arguments of `sin`, namely, `x`.

```{r, results='asis'}
term <- quote(integrate(sin, 0L, 2L*pi))
mathout(term)
```

Note that, on the Prolog end, the handler for `integrate/3` is rather rigid; it
accepts only these three arguments in that particular order, and without names,
that is, `integrate(sin, lower=0L, upper=2L*pi)`, would not print the desired
result.

To "canonicalize" function calls with named arguments and arguments in unusual
order, \pkg{mathml} provides an auxilliary function `canonical(f, drop)` that
reorders the argument list of calls to known functions and, if `drop=TRUE`,
drops the function names.

```{r}
term <- quote(integrate(lower=0L, upper=2L*pi, sin))
canonical(term)
```
